Exploring Income Inequality in US before and after financial crises: Analysis

### 2024-04-18 paper/paper.qmd
Update paper.qmd

---
title: "Exploring Income Inequality in US after and before financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in the United States from 2002 to 2019 using data from the United States Census and the World Inequality Database (WID). Throughout the paper, we will explore trends in income inequality, examining whether it is increasing or decreasing over time, and how the Great Recession of 2007-2009 affected income inequality. We will utilize data analysis and regression modeling to investigate these trends. Investigating these trends is significant, as it could assist policymakers or the government in developing strategies that could decrease the inequalities occurring within the country. As a result, this report may be used to help promote social and economic equity in the United States."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Introduction
Income inequality is a pressing issue not only in the United States but also globally. It pertains to the uneven distribution of income across a population, spotlighting disparities in financial well-being. Unlike wealth, which accounts for assets such as homes and stocks, income inequality focuses on earnings from various sources—wages, salaries, interest from savings, stock dividends, rental income, and profits from selling assets at a higher price than their purchase cost. This distinction is crucial for understanding the different facets of economic inequality. Therefore understanding inequality may provide insights for policymakers or researchers in contributing the problem.

>>>>

---
title: "Exploring Income Inequality in US before and after financial crises: Analysis"
subtitle: "Insights from 2002 to 2019"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/Exploring-Income-Inequality-in-US.git"
date: today
date-format: long
abstract: "This paper investigates income inequality in the United States from 2002 to 2019 using data from the United States Census and the World Inequality Database (WID). Throughout the paper, we will explore trends in income inequality, examining whether it is increasing or decreasing over time, and how the Great Recession of 2007-2009 affected income inequality. We will utilize data analysis and regression modeling to investigate these trends. Investigating these trends is significant, as it could assist policymakers or the government in developing strategies that could decrease the inequalities occurring within the country. As a result, this report may be used to help promote social and economic equity in the United States."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Introduction
Income inequality is a pressing issue not only in the United States but also globally. It pertains to the uneven distribution of income across a population, spotlighting disparities in financial well-being. Unlike wealth, which accounts for assets such as homes and stocks, income inequality focuses on earnings from various sources—wages, salaries, interest from savings, stock dividends, rental income, and profits from selling assets at a higher price than their purchase cost. This distinction is crucial for understanding the different facets of economic inequality. Therefore understanding inequality may provide insights for policymakers or researchers in contributing the problem.
